\documentclass[10pt,a4paper,ragged2e]{altacv}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}

\geometry{bottom=1.5cm,left=1.5cm,right=2.5cm}

\definecolor{Blue}{HTML}{1F4E79}
\definecolor{LightBlue}{HTML}{E6F0FA}

\colorlet{tagline}{olive}
\colorlet{heading}{olive}
\colorlet{accent}{Blue}
\colorlet{emphasis}{Blue}
\colorlet{body}{black}

\name{Aleksandr Kiriushin}{}
\tagline{Senior Software Engineer}
\personalinfo{
  \email{ak@everalerta.com}
  \phone{+46 76 109 9514}
  \location{Knivsta, Sweden}
  \linkedin{ak-everalerta}
}


\begin{document}
\makecvheader

\cvsection{Experience}

\cvevent{Senior Software Engineer (Bank \& BNPL - Platform Engineer, SRE, DevOps, Backend)}{Klarna, Stockholm, Sweden}{Apr 2021 -- Present}{}
\begin{itemize}
  \item Design, develop and maintain Klarna CI platform using Go, Kubernetes and AWS cloud.
  \item Develop compliance service in Python to secure production deployments.
  \item Actively participating in On Call duty, Datadog monitoring and alerts setup and internal support channel.
\end{itemize}

\divider

\cvevent{Senior Software Engineer (Payment Gateway - Backend \& Integrations)}{GA Tech Global, Limassol, Cyprus}{Dec 2019 -- Apr 2021}{}
\begin{itemize}
  \item Developed microservices for payment system integrations (Python).
  \item Built core balance alerting service (Slack + Google Drive API).
\end{itemize}

\divider

\cvevent{Software Engineer (Online Cinema - Encoder Backend)}{ivi.ru, Moscow, Russia}{Feb 2019 -- Dec 2019}{}
\begin{itemize}
  \item Maintained and enhanced content management platform (Django).
  \item Improved video encoder pipeline (Ffmpeg + Django) and Quality Control automation.
  \item Wrote SQL migrations and optimized analytical queries.
\end{itemize}

\divider

\cvevent{Software Engineer (CDN - Live Streaming Backend)}{CDNvideo, Moscow, Russia}{Apr 2017 -- Feb 2019}{}
\begin{itemize}
  \item Built backend for auto-configurable live streaming service.
  \item Led a team of 2 backend developers.
  \item Rewrote statistics service from Perl to Go with 2x performance improvement.
\end{itemize}

\divider

\cvevent{Junior Software Engineer (Startup - Backend, Frontend, Machine Learning)}{Semnotec, Moscow, Russia}{Nov 2015 -- Nov 2016}{}
\begin{itemize}
  \item Built integrations with multiple social networks and data collection backend.
  \item Built React JS dashboard to diplay data.
  \item Implemented a machine learning algorithm to classify websites by text.
\end{itemize}

\cvsection{Technical Skills}

\cvtag{Go}
\cvtag{Python}
\cvtag{SQL}
\cvtag{AWS}
\cvtag{Kubernetes}
\cvtag{Docker}
\cvtag{Terraform}
\cvtag{Datadog}
\cvtag{Grafana}
\cvtag{Linux}

\cvsection{Education}

\cvevent{B.Sc. Applied Mathematics \& Physics}{MIPT - Moscow Institute of Physics and Technology}{2010 -- 2018 (almost M.Sc.)}{}
Department of Control and Applied Mathematics

\end{document}
